Global case

### 2025-05-14 lipschitz 2025/Lipitschz.tex
update

	\subsection{Simplified model}

	The first simplified model (perhaps not a simplified one), is to use one variable to the difference of each two variables, which we use $y_i$ to  denote it: that is, if $x_i$ and $x'_i$ are two variables in $\mathcal{M}$ and $\mathcal{M}'$ representing the same node, then we set $y_i=x_i-x'_i$ and and $\hat{y}_i=\hat{x}_i-\hat{x}_i'$. The relation between $y_i$, $x'_i$ and $\hat{y}_i$ is $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i).$

	Given  $\gamma_i$ be the upper bound of $y_i$, then constraints for $\hat{y}_i$ are the follows:\begin{align*}
		\hat{y}_i \leq a \gamma_i \hspace*{2ex} &\wedge \hspace*{2ex}\hat{y}_i \geq y_i - a \gamma_i\\
		\hat{y}_i \geq (a-1) \gamma_i  \hspace*{2ex} &\wedge \hspace*{2ex} \hat{y}_i \leq y_i + (1-a) \gamma_i,
	\end{align*} where $a$ is a binary variable.

@@

	We will do experiments on two networks for MNIST dataset and another physical model.

	Among two MNIST $5\times 100$  full-connected DNN, one is a normally trained neural network and another is for trained for adversarial robustness. We call them MNIST $5\times100$-normal and MNIST $5\times 100$-DiffAI. They have the same structure: 5 hidden layer with 100 neurons each, 10 outputs and 784 inputs.

	The physical network is a simplified model with 10 input neurons, 26 output neurons, and 2 hidden layers with 50 neurons each.

>>>>

	\subsection{A Simplified model}

	To avoid above problem, we introduce a simplified model that is to use one variable to the difference of each two variables, which we use $y_i$ to  denote it: that is, if $x_i$ and $x'_i$ are two variables in $\mathcal{M}$ and $\mathcal{M}'$ representing the same node, then we set $y_i=x_i-x'_i$ and and $\hat{y}_i=\hat{x}_i-\hat{x}_i'$. The relation between $y_i$, $x'_i$ and $\hat{y}_i$ is $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i).$

	Given  $\gamma_i$ be the upper bound of $y_i$, then constraints for $\hat{y}_i$ are the follows:\begin{align*}
	\hat{y}_i &\leq a \gamma_i               &\quad \hat{y}_i &\geq y_i - a \gamma_i \\
	\hat{y}_i &\geq (a-1) \gamma_i           &\quad \hat{y}_i &\leq y_i + (1-a) \gamma_i
	\end{align*} where $a$ is a binary variable.

@@

	We will do experiments on two networks for MNIST dataset and another physical model. Two MNIST have the same structure. They are full-connected DNN with 5, 10 outputs and 784 inputs; each hidden layer has 100 neurons. One of them is a normally trained neural network and another is for trained for adversarial robustness. We call them MNIST $5\times100$-Normal and MNIST $5\times 100$-DiffAI. As the name shows MNIST $5\times 100$-DiffAI has a better robustness. The physical network is a simplified model with 10 input neurons, 26 output neurons, and 2 hidden layers with 50 neurons each.
